Spatial considerations in the analysis of biological conservation

### 2016-11-03 paper_v1.Rmd
Add files via upload

# 1.1 load prepared data files
#source_data("https://github.com/lexcomber/SpEcolCons2016/blob/master/SpEcolCons.RData?raw=True")
load('~/Desktop/my_docs_mac/leeds_work/research/conservation/anal/SpEcolCons.RData')

@@

# Acknowledgement Wildness Quality Index
# Kuiters, A. T., van Eupen, M., Carver, S., Fisher, M., Kun, Z., & Vancura, V. (2011). Wilderness register and indicator for Europe. Final Report - http://ec.europa.eu/environment/nature/natura2000/wilderness/pdf/Wilderness_register_indicator.pdf

>>>>

# 1.1 load prepared data files

#### **** You can download the data from the Github site *****
#### **** And then run source_data as below *****
# source_data("https://github.com/lexcomber/SpEcolCons2016/blob/master/SpEcolCons.RData?raw=True")

#### ***** OR load the data from a local file *****
load('~/Desktop/my_docs_mac/leeds_work/research/conservation/anal/SpEcolCons.RData')

@@

# Acknowledgement Wildness Quality Index
# Kuiters, A. T., van Eupen, M., Carver, S., Fisher, M., Kun, Z., & Vancura, V. (2013). Wilderness register and indicator for Europe. Final Report - http://ec.europa.eu/environment/nature/natura2000/wilderness/pdf/Wilderness_register_indicator.pdf
